\documentclass[line,11pt]{res}
\usepackage{multicol}
\usepackage[margin=1cm]{geometry}
\setlength{\resumewidth}{19.5cm}
\setlength{\columnsep}{1.5cm}
\newsectionwidth{0cm}

\begin{document}
\name{\Huge Ryan Serazin}
\address{8126 Lakeshore Rd\\ Burtchville, MI\\ 48059}
\address{(810) 304-6041\\ ryan.serazin@gmail.com\\ github.com/esapyr}

\begin{resume}
\begin{multicols}{2}

\section{\underline{\Large Education}}
B.S. of Computer Science with a minor in philosophy from The Rochester Institute of Technology expected May 2016. 

\section{\underline{\Large Personal Projects}}
\begin{itemize}
    \item Wrote a simple interpreter for McCarthy's original lisp in rust.
    \item Wrote an asynchronous graphical client server chat application in clojure using the aleph channel library.
    \item Hacked on a django application during RIT48 that connected students looking to build a team for a personal project. 
    \item Hacked on a flask app to help manage team and point information for an annual penny wars philanthropic event.
    \item Hacked on a clojure app to help manage service hour reporting.
\end{itemize}

\section{\underline{\Large Skills}}
\begin{itemize}
    \item \textbf{Languages:} Clojure/Clojurescript, Haskell, R, Rust, Python, Java, Javascript, HTML/CSS, PHP, C/C++
    \item \textbf{Libraries \& Applications:}  Elasticsearch, React, Angular, Postgresql, Flask, Django, Ring/Compojure, Nodejs, D3
    \item \textbf{Text Editors:} Vim, Eclipse, Lighttable, Visual Studio
    \item \textbf{Operating Systems:} GNU/Linux, Windows 8/7, OS X
    \item \textbf{Source Control:} git
\end{itemize}

\section{\underline{\Large Extracurriculars}}
\begin{itemize}
    \item Served as service chair for the Iota Beta chapter of Kappa Delta Rho from Fall 2013 to Spring 2014.
    \item Participated in HackMIT in 2013.
    \item Participated in the RIT48 hackathon in 2013.
\end{itemize}

\columnbreak

\section{\underline{\Large Internships \& Co-ops}}
\textit{\textbf{\\Showcase IDX (subsidiary of Tourbuzz)}\\ Atlanta GA \hfill{Summer-Fall 2015}}
\begin{itemize}
    \item Took over responsiblities for all Multiple Listing Service data, including importing and cleaning, after lead developer
          left to pursue his startup full time.  
    \item Wrote an administrative dashboard that let members of our small team quickly see the health of
          our entire system and individual MLS feeds, quickly change feed specific information, 
          write feed specific notes, add new data feeds, and have more fine grained control over data importing.
    \item Wrote an administrative tool that allowed non-technical members of our small team easily create and change
          the files we used to clean incoming MLS feed data.
    \item Wrote an tool that allowed real estate agents to personalize the CSS for our real estate search engine.
\end{itemize}

\textit{\textbf{Tourbuzz}\\ Atlanta GA \hfill{Summer 2014}}
\begin{itemize}
    \item Wrote an on the fly dieselpoint query language to elasticsearch query language transpiler in Clojure 
          using instaparse and a hand written context free grammar.
    \item Wrote a PHP app that routed incoming support calls to the highest priority support member available,
          while also finding the information we had internally on the incoming caller and sending it to that 
          support member over hipchat.
\end{itemize}

\textit{\textbf{The National Technical Institue for the Deaf}\\ Rochester NY \hfill{Summer 2013}}
\begin{itemize}
    \item Wrote and compiled a very limited graphical front end for editing ASL educational video with FFMPEG using Tkinter in Python.
    \item Maintained a course management system written in Javascript and ASP classic.
\end{itemize}

\textit{\textbf{Maclean-Fogg Component Solutions}\\ Royal Oak MI \hfill{Summer 2012}}
\begin{itemize}
    \item Designed and implemented a simple ASP.net website and backing database for all maintenance 
          department staff at Maclean-Fogg's facilities to track part usage.
\end{itemize}
\end{multicols}
\end{resume}
\end{document}
